On the properties of discs around accreting brown dwarfs

### 2010-05-25 BD_disc/paper.tex
Copy for Revision by TJH
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2282 25464f21-6099-402c-b30a-640f1d40d38b

XXXX Nathan - add disc structure equation here and remove walker references.

@@

As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
discussed in Section \ref{disc_flaring} BDD systems under vertical
hydrostatic equilibrium have highly flared discs. As discussed in
\cite{walker_2004} this increased flaring (when compared to CTTS
stars) leads to occultation at the star at lower inclination angles
and, therefore, significant changes to the SED. Increases in the
inclination angle, for these systems, quickly lead a significant
proportion of the stellar flux being intercepted, and reprocessed, by
the highly flared disc. This reprocessing will lead to a change in the
flux levels at the shorter, bluer, wavelengths as more stellar flux is
intercepted by the disc. It will also lead to significant changes in
the flux reaching the observer from the inner and outer regions of the
disc as the system approaches edge on. Also, as discussed in Section
\ref{disc_struct} the addition of dust sublimation leads to a change
in the shape of the inner edge, where the temperature is
sufficient. Figures \ref{no_sub_183_a} to \ref{sub_179_a}
\ref{sub_181_a} show a range in inner edge shapes, from flat walls
through concave to convex curves, caused by the radial density profile
of the disc and the dependence of the sublimation temperature on
density. This change in shape, as noted for Herbig Ae stars by
\cite{tannirkulam_2007} XX CHECK FOR A CTTS REFERENCESXXX, will lead
to changes in the characteristics of the SED, or derived IR excess,
with inclination angle \citep{tannirkulam_2007}, for close to face on
viewing angles.

@@

**THIS SECTION NEEDS TO BE SORTED**

>>>>

XXX Nathan - add disc structure equation here and remove walker references.

@@

As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
discussed in Section \ref{disc_flaring} BDD systems under vertical
hydrostatic equilibrium have highly flared discs. As discussed in
\cite{walker_2004} this increased flaring (when compared to CTTS
stars) leads to occultation at the star at lower inclination angles
and, therefore, significant changes to the SED. Increases in the
inclination angle, for these systems, quickly lead a significant
proportion of the stellar flux being intercepted, and reprocessed, by
the highly flared disc. This reprocessing will lead to a change in the
flux levels at the shorter, bluer, wavelengths as more stellar flux is
intercepted by the disc. It will also lead to significant changes in
the flux reaching the observer from the inner and outer regions of the
disc as the system approaches edge on. Also, as discussed in Section
\ref{disc_struct} the addition of dust sublimation leads to a change
in the shape of the inner edge, where the temperature is
sufficient. Figures \ref{no_sub_183_a} to \ref{sub_179_a}
\ref{sub_181_a} show a range in inner edge shapes, from flat walls
through concave to convex curves, caused by the radial density profile
of the disc and the dependence of the sublimation temperature on
density. This change in shape, as noted for Herbig Ae stars by
\cite{tannirkulam_2007} XXXCHECK FOR A CTTS REFERENCESXXX, will lead
to changes in the characteristics of the SED, or derived IR excess,
with inclination angle \citep{tannirkulam_2007}, for close to face on
viewing angles.

@@
